Neural Neural Textures Make Sim2Real Consistent

### 2022-06-23 CORL/appendix.tex
Added neural neural texture evaluation to appendix

@@

>>>>

	During evaluation, we render the neural neural texture onto a raster grid of pixels. Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image. Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table. This decreases video memory usage and speeds up calulations during inference.

@@

	\subsubsection{Videos}

		We have created animations using TRITON to see how consistency helps:

		https://youtu.be/fuTSta_M6NQ
